---
title: "Metrics for Data Management Campus"
output:
  pdf_document: default
  html_document: default
date: "2026-05-05"
---

```{r setup, include=FALSE}
library(dplyr)
library(tidyverse)
library(lubridate)
library(here)
```

## A) OpenLearnity

**Direct measures:**    

- **user_id**:	user identifier.      
- **module_title**: module title.    
- **last_login**: date of last login in the module. This variable overwrites each time the same user logs in.    

```{r, include=FALSE}
# load data
folder_path <- here::here("data/openlearnity")

files <- list.files(folder_path, pattern = "*.csv", full.names = TRUE)

df_openlearnity <- files |>
  map_dfr(~ read_csv(.x, show_col_types = FALSE) |>
            mutate(
              file_name = basename(.x),
              module = str_extract(basename(.x), "^[^_]+")  # extract prefix before _
            ))

# ensure correct date format
df_openlearnity <- df_openlearnity |>
  mutate(last_login = as.Date(last_login),
         date_joined = as.Date(date_joined)) 

# remove duplicate user_id + last_login combinations
df_openlearnity <- df_openlearnity |>
  distinct(username, name, last_login, module,.keep_all = T) |>
  group_by(module) |>
  arrange(module, desc(last_login)) |>
  select(id, username, name, email, last_login, date_joined, module) |>
  mutate(module_label = recode(module,
                               dmp = "Writing Data Management Plans",
                               documentation = "Data Documentation and Metadata",
                               fair = "Open Research Data, Research Data Management, and FAIR",
                               licences = "Data and Code Licenses",
                               openformats = "Open Formats and Code",
                               organisation = "Data Organization and Management",
                               publishing = "Data Publishing and Long-Term Preservation",
                               reproducibility = "Reproducibility and Code Management",
                               sensitive = "Sensitive Data",
                               storage = "Data Storage, Backup and Versioning"
  )) |>
  ungroup()

```

**Derived variables:**    

- **logged_users**: number of logged users per module during a specific period of time.    
Calculated as count of unique users per module.   

- **logged_users_week**: number of unique users per week for each module.         
Calculated as count of unique users grouped by week (from last_login) and module.  

```{r, include=FALSE}

# create weekly aggregation
df_openlearnity_weekly_activity <- df_openlearnity |>
  mutate(week = floor_date(last_login, unit = "week", week_start = 1)) |>
  group_by(module, week) |>
  summarise(n_users = n(), .groups = "drop") |>
  arrange(module, week) |>
  ungroup()

# define campaign start
campaign_dates <- tibble(
  module = c("dmp", "documentation", "fair", "licences", "openformats", "organisation", "publishing", "reproducibility", "sensitive", "storage"),
  campaign_start = as.Date(c("2026-03-23", "", "2026-02-23", "", "2026-04-14", "", "", "", "", ""))
)

```

##### Figure 1. Number of logged-in users per week for each module in OpenLearnity.
Selected time period: Jan 2026 up to now.   

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=7}
# plot
weekly_module_activity_plot <- ggplot(df_openlearnity_weekly_activity |>
              filter(week >= as.Date("2026-01-01")), 
            aes(x = week, y = n_users)) +
  geom_col(fill = "#2C7BB6", alpha = 0.8) +
  geom_vline(
    data = campaign_dates,
    aes(xintercept = campaign_start, color = "Marketing campaign"),
    linetype = "dashed",
    linewidth = 0.8
  ) +
  scale_x_date(
    date_breaks = "1 months",
    date_labels = "%b\n%Y"
  ) +
  facet_wrap(~ module, scales = "free_y", nrow = 2, ncol = 5,
             labeller = labeller(module = c(
               "dmp" = "Writing Data \nManagement Plans",
               "documentation" = "Data Documentation \nand Metadata",
               "fair" = "Open Research Data, \nRDM and FAIR",
               "licences" = "Data and \nCode Licences",
               "openformats" = "Open Formats \nand Code",
               "organisation" = "Data Organization \nand Management",
               "publishing" = "Data Publishing and \nLong-Term Preservation",
               "reproducibility" = "Reproducibility and \nCode Management",
               "sensitive" = "Sensitive Data",
               "storage" = "Data Storage, \nBackup and Versioning"
             ))) +
  scale_color_manual(name = "", values = c("Marketing campaign" = "red")) + 
  labs(x = "Week",
       y = "Number of users") +
  theme_minimal(base_size = 14) +
  theme(
    legend.position = "bottom",
    axis.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    strip.text = element_text(size = 13),
    plot.title = element_text(size = 16),
    axis.title = element_text(size = 13)
  )

weekly_module_activity_plot
```

```{r, include=FALSE}

# Number of users per module

# Select the time period: 
# Jan-Mar 2026

df_openlearnity_users <- df_openlearnity |>
  filter(last_login >= as.Date("2026-01-01") &
           last_login <= as.Date("2026-03-31")) |>
  distinct(username, name, module,.keep_all = T) |>
  group_by(module, module_label) |>
  summarise(total_users = n())

```
\newpage

## B) Matomo for OpenLearnity

**Direct measures:**    
Data from Page Titles.   

- **module_title**: module title.   
- **unique_pageviews**: unique page views of the module’s “About” page (counted once per session).   
- **entrances**: number of sessions that start on this page.    
- **actions_after_entry**: number of interactions (e.g., clicks, downloads, pageviews) performed after the session starts on this page.

**Derived variables:**   

- **engagement_per_entrance**: average number of user interactions generated after sessions start on the “About” page of a module.   
Calculated as actions_after_entry / entrances.  

```{r, include=FALSE}
# load data ----
matomo_pagetitles_20260101_20260331 <- read.csv(here("data", "matomo", "matomo_pagetitles_20260101_20260331.csv"))

modules <- c(
  "Open Research Data, Research Data Management, and FAIR",
  "Writing Data Management Plans",
  "Data Organization and Management",
  "Sensitive Data",
  "Data Documentation and Metadata",
  "Data Storage, Backup and Versioning",
  "Reproducibility and Code Management",
  "Open Formats and Code",
  "Data and Code Licenses",
  "Data Publishing and Long-Term Preservation"
)

matomo_jan_mar_2026 <- matomo_pagetitles_20260101_20260331 |>
  mutate(Label = str_remove(Label, "\\s*\\|\\s*OpenLearnity")) |>
  mutate(Label = str_trim(Label)) |>
  mutate(Label = case_when(
    #str_detect(Label, "Data Organisation and Management|Data Organization and Management") ~ "Data Organisation and Management",
    str_detect(Label, "Open Science and FAIR Data Principles|Open Research Data") ~ "Open Research Data, Research Data Management, and FAIR",
    TRUE ~ Label
  )) |>
  filter(Label %in% modules) |>
  group_by(Label) |>
  summarise(across(where(is.numeric), sum), .groups = "drop") |>
  rename(module_title = Label,
         unique_pageviews = Unique.Pageviews,
         pageviews = Pageviews,
         total_time_spent = Total.time.spent.by.visitors..in.seconds.,
         entrances = Entrances,
         actions_after_entry = Actions.after.entering.here) |>
  ungroup() |>
  mutate(
    # average time per page view
    # avg_time_on_page = total_time_spent / pageviews,
    # engagement per entrance
    engagement_per_entrance = actions_after_entry / entrances
  )

#select variables to plot ----
matomo_metrics <- matomo_jan_mar_2026 |>
  select(
    module_title,
    unique_pageviews,
    #avg_time_on_page,
    engagement_per_entrance
  )

# reshape for plotting ----
metrics_long_matomo <- matomo_metrics |>
  pivot_longer(
    cols = c(unique_pageviews, engagement_per_entrance),
    names_to = "metric",
    values_to = "value"
  ) |>
  mutate(
    metric = factor(metric,
                    levels = c("unique_pageviews",
                               "engagement_per_entrance")),
    
    metric_label = recode(metric,
                          unique_pageviews = "Unique pageviews \nin Matomo",
                          engagement_per_entrance = "Engagement per entrance \nin Matomo"
    )
  )

# get data from Openlearnity
metrics_long_openlearnity <- df_openlearnity_users |>
  mutate(
    metric = "total_users",
    metric_label = "Logged users \nin Open Learnity",
    value = total_users
  ) |>
  rename(module_title = module_label) |>
  select(module_title, metric, metric_label, value)

# combine datasets OL and Matomo
metrics_ol_matomo <- bind_rows(metrics_long_openlearnity, metrics_long_matomo) |>
  mutate(metric_label = factor(metric_label,
                               levels = c("Logged users \nin Open Learnity",
                                          "Unique pageviews \nin Matomo",
                                          "Engagement per entrance \nin Matomo")
  ))

```

##### Figure 2. User behaviour from Open Learnity and Matomo.
Selected time period: Jan-Mar 2026.  

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=11, fig.height=6, out.width="95%", fig.align="center"}

# plot combine OL and Matomo
ggplot(metrics_ol_matomo,
       aes(x = reorder(module_title, value),
           y = value)) +
  
  geom_col(aes(fill = metric)) +
  coord_flip() +
  
  facet_wrap(~metric_label, scales = "free_x") +
  
  scale_y_continuous(labels = scales::label_number(accuracy = 1)) +

  scale_fill_manual(values = c(
    "total_users" = "#7570B3",
    "unique_pageviews" = "#1B9E77",
    "engagement_per_entrance" = "#D95F02"
  )) +
  
  labs(
    x = "Module",
    y = "Metric",
    fill = ""
  ) +
  
  theme_minimal() +
  theme(
    legend.position = "none",
    axis.text.x = element_text(size = 11),
    axis.text.y = element_text(size = 11),
    strip.text = element_text(size = 12),
    plot.title = element_text(size = 14),
    axis.title = element_text(size = 12),
    legend.text = element_text(size = 11)
  )

```
\newpage

## C) Google Analytics for ORD Portal

**Direct measures:**      

- **page_title**: page title.   
- **views**: total number of page views. A proxy of intensity of use per page.   
- **active_users**: number of users who engaged with the page (i.e., session lasted 10 seconds or longer). A proxy of reach per page.   

```{r, include=FALSE}
# load data ----
google_analytics_20260101_20260331 <- read.csv(here("data", "google_analytics", "google_analytics_20260101_20260331.csv"))

ord_pages <- c(
  "Training Archive",
  "Open Research Data Portal",
  "Research Data Services Explorer",
  "Projects",
  "About",
  "Documents Archive"
)

google_analytics_jan_mar_2026 <- google_analytics_20260101_20260331 |>
  rename(page_title = Page.title.and.screen.class,
         views = Views,
         active_users = Active.users,
         views_per_user = Views.per.active.user,
         average_time_per_user = Average.engagement.time.per.active.user,
         event_count = Event.count,
         key_events = Key.events,
         total_revenue = Total.revenue) |>
  mutate(page_title = str_remove(page_title, " \\| Open Research Data Portal")) |>
  filter(page_title %in% ord_pages)

# calculate and select variables to plot ----
df_ga_metrics <- google_analytics_jan_mar_2026 |>
  select(
    page_title,
    views,
    active_users,
    views_per_user)

# reshape for plotting ----
metrics_long_ga <- pivot_longer(df_ga_metrics,
                        cols = c(views, active_users),
                        names_to = "metric",
                        values_to = "value") |>
  mutate(
    metric = factor(metric,
                    levels = c("active_users",
                               "views")),
    
    metric_label = recode(metric,
                          active_users = "Active users",
                          views = "Views"
    )
  )

```

##### Figure 3. Page views and active users for the ORD pages in Google Analytics.
Selected time period: Jan-Mar 2026.  

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=11, fig.height=6, out.width="95%", fig.align="center"}
# plot ----
ggplot(metrics_long_ga, 
       aes(x = reorder(page_title, value),
          y = value,
          fill = metric)) +
  geom_bar(stat = "identity", position = "dodge") +
  coord_flip() +
  scale_fill_discrete(labels = c(
    views = "Views",
    active_users = "Active users"
  )) +
  labs(
    y = "Metric",
    x = "ORD portal pages",
    fill = ""
  ) +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    axis.text.x = element_text(size = 11),
    axis.text.y = element_text(size = 11),
    strip.text = element_text(size = 12),
    plot.title = element_text(size = 14),
    axis.title = element_text(size = 12),
    legend.text = element_text(size = 11)
  )

```
\newpage

## D) Zenodo OER

**Direct measures:**  

- **record_id**: zenodo resource identifier.       
- **resource_title**: resource title.    
- **resource_type**: lesson, presentation, video_audio.   
- **views**: number of times resource was viewed.  
- **downloads**: number of times resource was downloaded.  

```{r, include=FALSE}
# load data
zenodo_records <- read.csv(here("data", "zenodo", "zenodo_records.csv"))

df_zenodo <- zenodo_records |>
  filter(
    str_starts(title, regex("Module", ignore_case = TRUE)) |
      str_starts(title, regex("Case study", ignore_case = TRUE)) |
      str_starts(title, regex("Introduction Video", ignore_case = TRUE))
  ) |>
  mutate(
    resource_group = case_when(
      str_starts(title, "Module") ~ "module",
      str_starts(title, "Case study") ~ "case_study",
      str_starts(title, "Introduction Video") ~ "intro_video",
      TRUE ~ NA_character_
    )
  ) |>
  filter(!is.na(resource_group)) |>
  mutate(
      resource_name = case_when(
        resource_group == "module" ~ str_extract(title, '(?<=Module \\").+?(?=\\")'),
        resource_group == "case_study" ~ str_remove(title, "^Case study animated video for learning module about "),
        resource_group == "intro_video" ~ str_remove(title, "^Introduction Video to "),
        TRUE ~ NA_character_
      ),
      resource_name = if_else(
        resource_name == "Data Management Plan",
        "Writing Data Management Plans",
        resource_name
      )
    )

# Prepare data
df_summary <- df_zenodo |>
  group_by(resource_name, resource_group) |>
  summarise(
    views = sum(views),
    downloads = sum(downloads),
    total = views + downloads,
    .groups = "drop"
  )

df_long <- df_summary |>
  pivot_longer(
    cols = c(views, downloads),
    names_to = "metric",
    values_to = "value"
  )

```

##### Figure 4. Total engagement by resource type and module in Zenodo.
Full record (no temporal filtering).   

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=11, fig.height=6, out.width="95%", fig.align="center"}

zenodo_fig2 <- ggplot(df_summary, aes(x = reorder(resource_name, total), 
                                      y = total, fill = resource_group)) +
  geom_col() +
  coord_flip() +
  scale_y_continuous(limits = c(0, 1251)) +
  scale_fill_discrete(labels = c(
    module = "Modules",
    intro_video = "Intro Videos",
    case_study = "Case Studies"
  )) +
  labs(
    x = "Module",
    y = "Total (views + downloads)",
    fill = "Resource type"
  ) +
    theme_minimal() +
    theme(
    legend.position = "bottom",
    axis.text.x = element_text(size = 11),
    axis.text.y = element_text(size = 11),
    legend.text = element_text(size = 11),
    plot.title = element_text(size = 14),
    plot.caption = element_text(
    hjust = 0.5,   # center
    size = 12      # bigger
  )
)
zenodo_fig2
```

\newpage

##### Figure 5. Number of views and downloads by resource type and module in Zenodo.
Full record (no temporal filtering).  

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=13, fig.height=7, out.width="100%", fig.align="center"}

custom_labels <- function(x) {
  ifelse(x == "Open Research Data, Research Data Management, and FAIR",
         "Open Research Data, Research \nData Management, and FAIR",
         x)
}

zenodo_fig3 <- ggplot(df_long, aes(
  x = resource_group,
  y = value,
  fill = metric
)) +
  geom_col(position = "stack", width = 0.3) +   # narrower bars
  scale_x_discrete(labels = c(
    "module" = "Modules",
    "intro_video" = "Intro Videos",
    "case_study" = "Case Studies"
  )) +
  scale_fill_discrete(labels = c(
    views = "Views",
    downloads = "Downloads"
  )) +
  facet_wrap(~ resource_name, 
            labeller = labeller(resource_name = custom_labels),
             scales = "free_x", 
             ncol = 4) +  # 5 panels per row
  labs(
    x = "Resource type",
    y = "Count",
    fill = ""
  ) +
  theme_minimal() +
  theme(legend.position = "bottom",
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(size = 10),
    legend.text = element_text(size = 10),
    plot.title = element_text(size = 14),
    strip.text = element_text(size = 10)
  )
zenodo_fig3

```


```{r, include=FALSE}
df_zenodo_other_resources <- zenodo_records |>
  filter(institution != "eth_domain_measure3")

df_other_summary <- df_zenodo_other_resources |>
  group_by(title, institution) |>
  summarise(
    views = sum(views),
    downloads = sum(downloads),
    total = views + downloads,
    .groups = "drop"
  )

df_other_long <- df_other_summary |>
  pivot_longer(
    cols = c(views, downloads),
    names_to = "metric",
    values_to = "value"
  )

```


\newpage

##### Figure 6. Number of views and downloads of other resources by institution in Zenodo.
Full record (no temporal filtering).  

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=7, out.width="90%", fig.align="center"}

zenodo_fig4 <- ggplot(df_other_long, aes(
  x = institution,
  y = value,
  fill = metric
)) +
  geom_col(position = "stack", width = 0.3) +   # narrower bars
  scale_x_discrete(labels = c(
    "empa" = "EMPA",
    "eth_library" = "ETH Library",
    "lib4ri" = "Lib4RI",
    "psi" = "PSI",
    "wsl" = "WSL"
  )) +
  scale_fill_discrete(labels = c(
    views = "Views",
    downloads = "Downloads"
  )) +
  labs(
    x = "Institution",
    y = "Count",
    fill = ""
  ) +
  theme_minimal() +
  theme(legend.position = "bottom",
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(size = 10),
    legend.text = element_text(size = 10),
    plot.title = element_text(size = 14),
    strip.text = element_text(size = 10)
  )
zenodo_fig4

```

