---
title: "Metrics for the Data Management Campus modules"
output:
  html_document: default
  pdf_document: default
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
library(dplyr)
library(tidyverse)
library(lubridate)
library(here)
library(patchwork)
library(ggtext)
```

<br>

This document loads and visualizes data on the use of modules from the Data Management Campus.  
The data are obtained from four sources: OpenLearnity, Matomo (metrics on the OpenLearnity modules), Google Analytics (metrics on the ORD Portal), and Zenodo OER.  
A list of the variables used in the analysis is provided below.  

```{r, include=FALSE}

# OpenLearnity ----
# Direct measures: user_id, module_title, last_login
# Derived variables: logged_users, logged_users_week

# load data
folder_path <- here::here("data/openlearnity")

files <- list.files(folder_path, pattern = "*.csv", full.names = TRUE)

df_openlearnity <- files |>
  map_dfr(~ read_csv(.x, show_col_types = FALSE) |>
            mutate(
              file_name = basename(.x),
              module = str_extract(basename(.x), "^[^_]+")  # extract prefix before _
            ))

# ensure correct date format
df_openlearnity <- df_openlearnity |>
  mutate(last_login = as.Date(last_login),
         date_joined = as.Date(date_joined)) 

# remove duplicate user_id + last_login combinations
df_openlearnity <- df_openlearnity |>
  distinct(username, name, last_login, module,.keep_all = T) |>
  group_by(module) |>
  arrange(module, desc(last_login)) |>
  select(id, username, name, email, last_login, date_joined, module) |>
  mutate(module_label = recode(module,
                               dmp = "Writing Data Management Plans",
                               documentation = "Data Documentation and Metadata",
                               fair = "Open Research Data, Research Data Management, and FAIR",
                               licences = "Data and Code Licenses",
                               openformats = "Open Formats and Code",
                               organisation = "Data Organization and Management",
                               publishing = "Data Publishing and Long-Term Preservation",
                               reproducibility = "Reproducibility and Code Management",
                               sensitive = "Sensitive Data",
                               storage = "Data Storage, Backup and Versioning"
  )) |>
  ungroup()

```

```{r, include=FALSE}

# Derived variables: Number of logged-in users per week and module

# create weekly aggregation
df_openlearnity_weekly_activity <- df_openlearnity |>
  mutate(week = floor_date(last_login, unit = "week", week_start = 1)) |>
  group_by(module, week) |>
  summarise(n_users = n(), .groups = "drop") |>
  arrange(module, week) |>
  ungroup()

# define campaign start
campaign_dates <- tibble(
  module = c("dmp", "documentation", "fair", "licences", "openformats", "organisation", "publishing", "reproducibility", "sensitive", "storage"),
  campaign_start = as.Date(c("2026-03-23", "", "2026-02-23", "", "2026-04-14", "", "", "", "", ""))
)

```
<br>

##### 1. Number of logged-in users per week for each module in OpenLearnity

<br>
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=7,out.width="100%", fig.align="center"}

fig1 <- ggplot(df_openlearnity_weekly_activity |>
              filter(week >= as.Date("2026-01-01")), 
            aes(x = week, y = n_users)) +
  geom_col(fill = "#2C7BB6", alpha = 0.8) +
  geom_vline(
    data = campaign_dates,
    aes(xintercept = campaign_start, color = "Marketing campaign"),
    linetype = "dashed",
    linewidth = 0.8
  ) +
  scale_x_date(
    date_breaks = "1 months",
    date_labels = "%b\n%Y"
  ) +
  facet_wrap(~ module, scales = "free_y", nrow = 2, ncol = 5,
             labeller = labeller(module = c(
               "dmp" = "Writing Data \nManagement Plans",
               "documentation" = "Data Documentation \nand Metadata",
               "fair" = "Open Research Data, \nRDM and FAIR",
               "licences" = "Data and \nCode Licences",
               "openformats" = "Open Formats \nand Code",
               "organisation" = "Data Organization \nand Management",
               "publishing" = "Data Publishing and \nLong-Term Preservation",
               "reproducibility" = "Reproducibility and \nCode Management",
               "sensitive" = "Sensitive Data",
               "storage" = "Data Storage, \nBackup and Versioning"
             ))) +
  scale_color_manual(name = "", values = c("Marketing campaign" = "red")) + 
  labs(x = "Week",
       y = "Number of users",
       caption = "<b>Selected time period:</b> Jan 2026 up to now.<br>
       <b>Data source:</b> OpenLearnity.") +
  theme_minimal(base_size = 14) +
  theme(
    legend.position = "bottom",
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(size = 10),
    strip.text = element_text(size = 11),
    plot.title = element_text(size = 16),
    axis.title = element_text(size = 10),
    #plot.caption = element_text(hjust = 0, face = "bold", size = 12)
    plot.caption = element_markdown(size = 12, hjust = 1, lineheight = 1.3)
  )

fig1 

```
<br>

Figure 1 shows weekly user activity across modules based on OpenLearnity enrollment data.     
Blue bars represent the *logged_users_week* variable (number of unique users logging in per module each week).   
Weekly user activity is generally low, ranging from 0 to about 6 users per week depending on the module, with no strong differences in magnitude over time.   
Red dashed lines indicate the timing of the marketing campaign, corresponding to the week when the modules were advertised on ETH Campus Channel screens. No systematic change in activity is visible around the campaign period.

```{r, include=FALSE}

# Derived variables: Number of users per module

# Select the time period: 
# Jan-Mar 2026

df_openlearnity_users <- df_openlearnity |>
  filter(last_login >= as.Date("2026-01-01") &
           last_login <= as.Date("2026-03-31")) |>
  distinct(username, name, module,.keep_all = T) |>
  group_by(module, module_label) |>
  summarise(total_users = n())

```
\newpage

```{r, include=FALSE}

# Matomo ----
# Direct measures: module_title, unique_pageviews, entrances, actions_after_entry, bounces
# Derived variables: engagement_per_entrance, bounces rate

# unique_pageviews: proxy for reach / interest
# engagement_per_entrance: proxy for depth of interaction

# load data ----
matomo_pages_20260101_20260331 <- read.csv(here("data", "matomo", "matomo_pages_20260101_20260331.csv"))

pages <- c(
  "/courses/course-v1:open fair data/about",
  "/courses/course-v1:data management plan/about",
  "/courses/course-v1:open data organisation/about",
  "/courses/course-v1:ETH sensitive data/about",
  "/courses/course-v1:ETH documentation metadata/about",
  "/courses/course-v1:storage backup versioning/about",
  "/courses/course-v1:ETH code reproducibility/about",
  "/courses/course-v1:open formats code/about",
  "/courses/course-v1:ETH data licences/about",
  "/courses/course-v1:ETH RDM-01 2024/about"
)

modules <- c(
  "Open Research Data, Research Data Management, and FAIR",
  "Writing Data Management Plans",
  "Data Organization and Management",
  "Sensitive Data",
  "Data Documentation and Metadata",
  "Data Storage, Backup and Versioning",
  "Reproducibility and Code Management",
  "Open Formats and Code",
  "Data and Code Licenses",
  "Data Publishing and Long-Term Preservation"
)

module_map <- setNames(modules, pages)

# Extract and rename
matomo_jan_mar_2026 <- matomo_pages_20260101_20260331 |>
  filter(Label %in% pages) |>
  mutate(Label = module_map[Label]) |>
  rename(module_title = Label,
         unique_pageviews = Unique.Pageviews,
         pageviews = Pageviews,
         total_time_spent = Total.time.spent.by.visitors..in.seconds.,
         entrances = Entrances,
         bounces = Bounces,
         actions_after_entry = Actions.after.entering.here) |>
  mutate(
    engagement_per_entrance = actions_after_entry / entrances,
    bounce_rate = bounces / entrances * 100
  )

#select variables to plot ----
matomo_metrics <- matomo_jan_mar_2026 |>
  select(
    module_title,
    unique_pageviews,
    engagement_per_entrance,
    bounce_rate
  )

# reshape for plotting ----
metrics_long_matomo <- matomo_metrics |>
  pivot_longer(
    cols = c(unique_pageviews, engagement_per_entrance, bounce_rate),
    names_to = "metric",
    values_to = "value"
  ) |>
  mutate(
    metric = factor(metric,
                    levels = c("unique_pageviews",
                               "engagement_per_entrance",
                               "bounce_rate")),
    
    metric_label = recode(metric,
                          unique_pageviews = "Unique pageviews",
                          engagement_per_entrance = "Engagement per entrance",
                          bounce_rate = "Bounce rate"
    )
  )

# get data from Openlearnity
metrics_long_openlearnity <- df_openlearnity_users |>
  mutate(
    metric = "total_users",
    metric_label = "Logged users",
    value = total_users
  ) |>
  rename(module_title = module_label) |>
  select(module_title, metric, metric_label, value)

# combine datasets OL and Matomo
metrics_ol_matomo <- bind_rows(metrics_long_openlearnity, metrics_long_matomo) |>
  mutate(metric_label = factor(metric_label,
                               levels = c("Logged users",
                                          "Unique pageviews",
                                          "Engagement per entrance",
                                          "Bounce rate")
  ))

```
<br>

##### 2. User behaviour from Open Learnity and Matomo.

<br>
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="100%", fig.align="center"}

fig2 <- ggplot(metrics_ol_matomo,
       aes(x = reorder(module_title, value),
           y = value)) +
  
  geom_col(aes(fill = metric)) +
  coord_flip() +
  
  facet_wrap(~metric_label, scales = "free_x", nrow = 1, strip.position = "bottom") +
  
  scale_y_continuous(labels = scales::label_number(accuracy = 1)) +
  
  scale_fill_manual(values = c(
    "total_users" = "#7570B3",
    "unique_pageviews" = "#1B9E77",
    "engagement_per_entrance" = "#D95F02",
    "bounce_rate" = "#E6AB02"
  )) +
  
  labs(
    title = "",
    x = "Module",
    y = "",
    fill = "",
    caption = "<b>Selected time period:</b> Jan-Mar 2026.<br>
       <b>Data source:</b> OpenLearnity and Matomo."
  ) +
  theme_minimal() +
  theme(
    legend.position = "none",
    axis.text.x = element_text(size = 11),
    axis.text.y = element_text(size = 11),
    strip.text = element_text(size = 11),
    strip.placement = "outside",
    strip.background = element_blank(),
    plot.title = element_text(size = 13),
    axis.title = element_text(size = 11),
    plot.caption = element_markdown(size = 12, hjust = 1, lineheight = 1.3),
  )

fig2

```

<br>

Figure 2 shows user behaviour across modules using OpenLearnity user data and Matomo analytics. Four indicators are displayed per module: *logged_users* (Open Learnity enrollment), *unique_pageviews*, *engagement_per_entrance*, and *bounce_rate* (Matomo metrics).    

The four metrics together describe different dimensions of user behaviour:    
Logged users represent the number of participants enrolled in each module.       
Unique pageviews refer to the number of distinct page views of the module’s “About” page (counted once per session).    
Engagement per entrance is the average number of user interactions after sessions start on the “About” page of a module. This serves as a proxy for content depth and user interest.   
Bounce rate is the proportion of single-page sessions with no further interaction.   

Best-performing module:    
The Data and Code Licenses module shows the strongest overall engagement in the dataset. It combines a relatively high number of unique pageviews (72) with the highest engagement per entrance (10.1 actions per session), indicating that users interact intensively once they access the content. In addition, it has one of the lowest bounce rates (21%), suggesting strong user retention.   

Lowest-performing module:    
The Writing Data Management Plans module shows the weakest engagement profile. Although it receives a moderate number of unique pageviews (34), it has the lowest engagement per entrance (3.87 actions per session), indicating limited interaction once users enter the module. Its bounce rate (40%) is also relatively high, suggesting that a substantial proportion of users leave without further interactions.     
Limitations:  
Data is based on the *About* pages and does not capture complete user journeys across the platform, including navigation through home pages or across modules.  
The indicators are best interpreted as proxies for interaction intensity rather than direct measures of course progression or learning outcomes.  

\newpage
```{r, include=FALSE}

# Google Analytics
# Direct measures: page_title, views, active_users  

# load data
google_analytics_20260101_20260331 <- read.csv(here("data", "google_analytics", "google_analytics_20260101_20260331.csv"))

ord_pages <- c(
  "Training Archive",
  "Open Research Data Portal",
  "Research Data Services Explorer",
  "Projects",
  "About",
  "Documents Archive"
)

google_analytics_jan_mar_2026 <- google_analytics_20260101_20260331 |>
  rename(page_title = Page.title.and.screen.class,
         views = Views,
         active_users = Active.users,
         views_per_user = Views.per.active.user,
         average_time_per_user = Average.engagement.time.per.active.user,
         event_count = Event.count,
         key_events = Key.events,
         total_revenue = Total.revenue) |>
  mutate(page_title = str_remove(page_title, " \\| Open Research Data Portal")) |>
  filter(page_title %in% ord_pages) |>
  mutate(page_title = recode(page_title,
                             "Training Archive" = "Training",
                             "Documents Archive" = "Documents",
                             "Research Data Services Explorer" = "Services",
                             "Open Research Data Portal" = "Home")) |>
  mutate(page_title = factor(page_title,
                             levels = c(
                               "Home",
                               "Projects",
                               "Training",
                               "Services",
                               "Documents",
                               "About"
                             )))

# calculate and select variables to plot ----
df_ga_metrics <- google_analytics_jan_mar_2026 |>
  select(
    page_title,
    views,
    active_users)

# reshape for plotting ----
metrics_long_ga <- pivot_longer(df_ga_metrics,
                        cols = c(views, active_users),
                        names_to = "metric",
                        values_to = "value") |>
  mutate(
    metric = factor(metric,
                    levels = c("active_users",
                               "views")),
    
    metric_label = recode(metric,
                          active_users = "Active users",
                          views = "Views"
    )
  )

```
<br>

##### 3. Page views and active users for the ORD pages in Google Analytics.

<br>
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=11, fig.height=6, out.width="95%", fig.align="center"}

fig3 <- ggplot(metrics_long_ga, 
       aes(x = reorder(page_title, value),
          y = value,
          fill = metric)) +
  geom_bar(stat = "identity", position = "dodge") +
  coord_flip() +
  scale_fill_discrete(labels = c(
    views = "Views",
    active_users = "Active users"
  )) +
  labs(
    y = "Metric",
    x = "ORD portal pages",
    caption = "<b>Selected time period:</b> Jan-Mar 2026.<br>
       <b>Data source:</b> Google Analytics.") +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    axis.text.x = element_text(size = 11),
    axis.text.y = element_text(size = 11),
    strip.text = element_text(size = 12),
    plot.title = element_text(size = 14),
    axis.title = element_text(size = 12),
    legend.text = element_text(size = 11),
    plot.caption = element_markdown(size = 12, hjust = 1, lineheight = 1.3)
  )

fig3

```
<br>

Figure 3 shows the distribution of user engagement across ORD portal pages based on Google Analytics data.  
Blue and red bars represent *views* (total number of page views; a proxy of intensity of use per page) and *active_users* (number of users whose session lasted at least 10 seconds; a proxy of reach per page) for each ORD portal page, obtained from Google Analytics.   
The Training page corresponds to the Data Management Campus and shows the highest number of views (1,000) but fewer active users (374), indicating high engagement per user (i.e., strong content usage).  

\newpage
```{r, include=FALSE}

# Zenodo ----
# Direct measures: record_id, resource_title, resource_type, views, downloads

# load data
zenodo_records <- read.csv(here("data", "zenodo", "zenodo_records.csv"))

df_zenodo <- zenodo_records |>
  filter(
    str_starts(title, regex("Module", ignore_case = TRUE)) |
      str_starts(title, regex("Case study", ignore_case = TRUE)) |
      str_starts(title, regex("Introduction Video", ignore_case = TRUE))
  ) |>
  mutate(
    resource_group = case_when(
      str_starts(title, "Module") ~ "module",
      str_starts(title, "Case study") ~ "case_study",
      str_starts(title, "Introduction Video") ~ "intro_video",
      TRUE ~ NA_character_
    )
  ) |>
  filter(!is.na(resource_group)) |>
  mutate(
      resource_name = case_when(
        resource_group == "module" ~ str_extract(title, '(?<=Module \\").+?(?=\\")'),
        resource_group == "case_study" ~ str_remove(title, "^Case study animated video for learning module about "),
        resource_group == "intro_video" ~ str_remove(title, "^Introduction Video to "),
        TRUE ~ NA_character_
      ),
      resource_name = if_else(
        resource_name == "Data Management Plan",
        "Writing Data Management Plans",
        resource_name
      )
    )

# Prepare data
df_summary <- df_zenodo |>
  group_by(resource_name, resource_group) |>
  summarise(
    views = sum(views),
    downloads = sum(downloads),
    total = views + downloads,
    .groups = "drop"
  )

df_long <- df_summary |>
  pivot_longer(
    cols = c(views, downloads),
    names_to = "metric",
    values_to = "value"
  )

```
<br>

##### 4. Total engagement by resource type and module in Zenodo.

<br>
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=11, fig.height=6, out.width="95%", fig.align="center"}

fig4 <- ggplot(df_summary, aes(x = reorder(resource_name, total), 
                                      y = total, fill = resource_group)) +
  geom_col() +
  coord_flip() +
  scale_y_continuous(limits = c(0, 1251)) +
  scale_fill_discrete(labels = c(
    module = "Modules",
    intro_video = "Intro Videos",
    case_study = "Case Studies"
  )) +
  labs(
    x = "Module",
    y = "Total (views + downloads)",
    fill = "Resource type",
    caption = "<b>Selected time period:</b> Full record (no temporal filtering).<br>
       <b>Data source:</b> Zenodo."
    ) +
    theme_minimal() +
    theme(
    legend.position = "bottom",
    axis.text.x = element_text(size = 11),
    axis.text.y = element_text(size = 11),
    legend.text = element_text(size = 11),
    plot.title = element_text(size = 14),
    #plot.caption = element_text(hjust = 0.5, size = 12)     
    plot.caption = element_markdown(size = 12, hjust = 1, lineheight = 1.3)
)
fig4

```
<br>

Figure 4 displays the combined total of *views* and *downloads* per resource, as recorded in Zenodo.  
Blue, green, and red bars represent different resource types: modules, introductory videos, and case studies, respectively. Only 6 of the 10 modules include associated case studies (PowToon videos).   
Introductory videos account for the majority of total engagement, whereas modules generally receive fewer views and downloads.  

<br>

\newpage

##### 5. Number of views and downloads by resource type and module in Zenodo.

<br>

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=8, out.width="90%", fig.align="center"}

custom_labels <- function(x) {
  ifelse(x == "Open Research Data, Research Data Management, and FAIR",
         "Open Research Data, Research \nData Management, and FAIR",
         x)
}

fig5 <- ggplot(df_long, aes(
  x = resource_group,
  y = value,
  fill = metric
)) +
  geom_col(position = "stack", width = 0.3) +   # narrower bars
  scale_x_discrete(labels = c(
    "module" = "Modules",
    "intro_video" = "Intro Videos",
    "case_study" = "Case Studies"
  )) +
  scale_fill_discrete(labels = c(
    views = "Views",
    downloads = "Downloads"
  )) +
  facet_wrap(~ resource_name, 
            labeller = labeller(resource_name = custom_labels),
             scales = "free_x", 
             ncol = 3) +  # 5 panels per row
  labs(
    x = "Resource type",
    y = "Count",
    fill = "",
    caption = "<b>Selected time period:</b> Full record (no temporal filtering).<br>
       <b>Data source:</b> Zenodo."
  ) +
  theme_minimal() +
  theme(legend.position = "bottom",
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(size = 10),
    legend.text = element_text(size = 10),
    plot.title = element_text(size = 14),
    strip.text = element_text(size = 10),
    plot.caption = element_markdown(size = 11, hjust = 1, lineheight = 1.3)
  )

fig5

```
<br>

Figure 5 shows the distribution of *views* and *downloads* per resource type (modules, introductory videos, and case studies), as recorded in Zenodo.   
Blue and red bars represent views and downloads, respectively. Each panel corresponds to a module content, allowing comparison across resource types within the same module. Also notice that only 6 of the 10 modules include associated case studies (PowToon videos).  
Introductory videos account for the majority of total engagement, whereas modules generally receive fewer views and downloads.  

\newpage
```{r, include=FALSE}
df_zenodo_other_resources <- zenodo_records |>
  filter(institution != "eth_domain_measure3")

df_other_summary <- df_zenodo_other_resources |>
  group_by(title, institution) |>
  summarise(
    views = sum(views),
    downloads = sum(downloads),
    total = views + downloads,
    .groups = "drop"
  )

df_other_long <- df_other_summary |>
  pivot_longer(
    cols = c(views, downloads),
    names_to = "metric",
    values_to = "value"
  )

```

<br>

##### 6. Number of views and downloads of other resources by institution in Zenodo.

<br>
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=7, out.width="85%", fig.align="center"}

fig6 <- ggplot(df_other_long, aes(
  x = institution,
  y = value,
  fill = metric
)) +
  geom_col(position = "stack", width = 0.3) +   # narrower bars
  scale_x_discrete(labels = c(
    "empa" = "EMPA",
    "eth_library" = "ETH Library",
    "lib4ri" = "Lib4RI",
    "psi" = "PSI",
    "wsl" = "WSL"
  )) +
  scale_fill_discrete(labels = c(
    views = "Views",
    downloads = "Downloads"
  )) +
  labs(
    x = "Institution of the OER author",
    y = "Count",
    fill = "",
    caption = "<b>Selected time period:</b> Full record (no temporal filtering).<br>
    <b>Data source:</b> Zenodo."
  ) +
  theme_minimal() +
  theme(legend.position = "bottom",
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(size = 10),
    legend.text = element_text(size = 10),
    plot.title = element_text(size = 14),
    strip.text = element_text(size = 10),
    plot.caption = element_markdown(size = 13, hjust = 1, lineheight = 1.3)
  )

fig6

```
<br>

Figure 6 shows the distribution of *views* and *downloads* for other resources (i.e., non-module-related content) in Zenodo, aggregated by institution of the resource author (i.e., the institution that created the content).  
Blue and red bars represent views and downloads, respectively. Values are stacked to show total engagement per institution.  
The high number of views and downloads for EMPA corresponds to the series of video presentations on Research Data Management by Matthias Roesslein.  

<br>
\newpage

##### List of variables used for the analysis of Data Management Campus module usage

<br>

| indicator | source | estimation | description |
|-----------|--------|-------------|-------------|
| **user_id** | openlearnity | direct measure | user identifier |
| **module_title** | openlearnity | direct measure | module title |
| **last_login** | openlearnity | direct measure | date of last login in the module. This variable is overwritten each time the same user logs in. |
| **logged_users_week** | openlearnity | calculated as count of unique users grouped by week (from last_login) and module | number of unique users per week for each module |
| **logged_users** | openlearnity | calculated as count of unique users per module | number of logged users per module during a specific period of time |
| **module_title** | matomo_ol | direct measure | module title |
| **unique_pageviews** | matomo_ol | direct measure | number of page views counted once per session; unique page views of the module’s “About” page |
| **entrances** | matomo_ol | direct measure | number of sessions starting on the “About” page |
| **actions_after_entry** | matomo_ol | direct measure | number of interactions (clicks, downloads, pageviews) performed after session start on the “About” page |
| **bounces** | matomo_ol | direct measure | sessions where the user leaves after viewing only one page |
| **engagement_per_entrance** | matomo_ol | calculated as actions_after_entry / entrances | average number of user interactions after session start on the “About” page |
| **bounce_rate** | matomo_ol | calculated as bounces / entrances | proportion of visits where users leave after one page |
| **page_title** | google_analytics_ord | direct measure | title of the pages in the ORD Portal |
| **views** | google_analytics_ord | direct measure | total number of page views; proxy of intensity of use per page |
| **active_users** | google_analytics_ord | direct measure | number of users who engaged with the page (session last at least 10 seconds) |
| **record_id** | zenodo | direct measure | Zenodo resource identifier |
| **resource_title** | zenodo | direct measure | resource title |
| **resource_type** | zenodo | direct measure | type of resource (lesson, presentation, video/audio) |
| **views** | zenodo | direct measure | number of times resource was viewed |
| **downloads** | zenodo | direct measure | number of times resource was downloaded |

<br>
